MINOS Handover Plots

### 2023-10-09 minos/validation/handovers.Rmd
First stab at chronic disease module

density_ridges(income.spag, 'hh_income',
               save=TRUE, 
               save.path=save.path)

@@

>>>>

density_ridges(income.spag, 'hh_income',
               save=shall.we.save, 
               save.path=save.path)

@@

## Chronic Disease

```{r}
handover_ordinal(raw.dat, base.dat, var = 'chron_disease', save = shall.we.save)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, chron_disease) %>%
  filter(!chron_disease %in% miss.values)
base.s <- base.dat %>%
  select(pidp, age, time, chron_disease) %>%
  filter(!chron_disease %in% miss.values)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'chron_disease',
               save = shall.we.save,
               save.path = save.path)

density_ridges(spag, 'chron_disease',
               save=shall.we.save, 
               save.path=save.path)

pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
spaghetti_plot(spag.sample, 'chron_disease',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```
